Dynein walks like an Imperial AT-ST

### 2018-08-10 papers/paper/paper.tex
Add trajectory seed # specification in paper_params; add arrows to trajectory plot
Slightly perfect arrow placement for trajectory plot.
Add unbinding rate vs L plot to paper.tex.
Change up makefile and paper.tex to make room for new figures, remove old figures

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/paper_static_time_vs_length}
\caption{Heatmap of relationship between step length and time.}
\label{fig:duration-length}
\end{figure}

@@

\begin{figure*}[tbhp]
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_static_step_length_histogram}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_exponential_step_length_histogram}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_static_displacement_histogram}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_exponential_displacement_histogram}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_static_displacement_vs_step_length}
    \subcaption{Static unbinding rate}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../../plots/paper_exponential_displacement_vs_step_length}
    \subcaption{Exponential unbinding rate}
  \end{subfigure}
\caption{Stepping behavior of static and exponential models, with parameters shown in Table \ref{tab:staticparams}.}
\label{fig:lengthhist}
\end{figure*}

\begin{figure*}[tbhp]
    \includegraphics[width=0.5\linewidth]{../../plots/paper_static_foot_order_histogram}
    \includegraphics[width=0.5\linewidth]{../../plots/paper_exponential_foot_order_histogram}
\caption{The left plot is the $C=0$ case where the unbinding rate is
  independent of angle.  Here ``alternating'' means that the binding
  domain which did not move last time moved this time.  Passing means
  that the moving foot was behind, and ended up in front.}
\label{fig:steppingorder}
\end{figure*}

@@

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/paper_trajectory_plot.pdf}
\caption{\textbf{Model achieves forward-directed processivity.} \textit{Top view:} x-position of near and far binding domains during a 10 $\mu s$ simulation at high kinetic parameters of $k_b = \trajectorykb s^{-1}$ and $k_{ub} = \trajectorykub s^{-1}$. \textit{Middle view:} Cartoon snapshot of model at time indicated by bound binding domain. Teal lines correspond to the microtubule. \textit{Bottom view:} y-projection.}
\label{fig:trajectory}
\end{figure}

@@

\subsection{Elliott}
\begin{enumerate}
\item Document carefully where all figures and data comes from.
\item Describe our algorithm in sufficient detail.
\item Fix stepping analysis python module to categorize zero-length
  steps separately from other steps, particularly in terms of stepping
  times.  Alternately, change C++ to make it possible to identify
  which foot lifted if it didn't move.
\item Update plotting scripts to use stepping analysis python module,
  or other modules.
\item Write up how we estimate one-bound/bothbound time ratio from
  processivity.  Ensure simulation obeys this?
\item Keep trying to get data from Yildiz.
\item Add force-dependent plots to compare with yildiz?
\item Figure out which of the model-em subfigures to include/remove
\item add cartoon back to trajectory plot
\end{enumerate}

>>>>

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/paper_time_vs_length}
\caption{Heatmap of relationship between step length and time.}
\label{fig:duration-length}
\end{figure}

@@

%% \begin{figure*}[tbhp]
%%   \begin{subfigure}{0.5\textwidth}
%%     \centering
%%     \includegraphics[width=\linewidth]{../../plots/paper_static_step_length_histogram}
%%   \end{subfigure}%
%%   \begin{subfigure}{0.5\textwidth}
%%     \centering
%%     \includegraphics[width=\linewidth]{../../plots/paper_exponential_step_length_histogram}
%%   \end{subfigure}
%%   \begin{subfigure}{0.5\textwidth}
%%     \centering
%%     \includegraphics[width=\linewidth]{../../plots/paper_static_displacement_histogram}
%%   \end{subfigure}%
%%   \begin{subfigure}{0.5\textwidth}
%%     \centering
%%     \includegraphics[width=\linewidth]{../../plots/paper_exponential_displacement_histogram}
%%   \end{subfigure}
%%   \begin{subfigure}{0.5\textwidth}
%%     \centering
%%     \includegraphics[width=\linewidth]{../../plots/paper_static_displacement_vs_step_length}
%%     \subcaption{Static unbinding rate}
%%   \end{subfigure}%
%%   \begin{subfigure}{0.5\textwidth}
%%     \centering
%%     \includegraphics[width=\linewidth]{../../plots/paper_exponential_displacement_vs_step_length}
%%     \subcaption{Exponential unbinding rate}
%%   \end{subfigure}
%% \caption{Stepping behavior of static and exponential models, with parameters shown in Table \ref{tab:staticparams}.}
%% \label{fig:lengthhist}
%% \end{figure*}

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=0.5\linewidth]{../../plots/paper_stepping_length_histogram}
  \includegraphics[width=0.5\linewidth]{../../plots/paper_dwell_time_histogram}
  \includegraphics[width=0.5\linewidth]{../../plots/paper_displacement_vs_step_length.pdf}
  \includegraphics[width=0.5\linewidth]{../../plots/paper_unbinding_probability_vs_L.pdf}
\caption{\textbf{Basic behavior of our model}}
\label{fig:}
\end{figure}

\begin{figure}[tbhp]
  \centering
  \includegraphics[width=0.5\linewidth]{../../plots/paper_onebound_vs_steplength.pdf}
  \includegraphics[width=0.5\linewidth]{../../plots/paper_onebound_histogram.pdf}
  \includegraphics[width=0.5\linewidth]{../../plots/paper_initial_vs_final_displacement.pdf}
\caption{\textbf{Does our model capture dynamics a markov model wouldn't?}}
\label{fig:}
\end{figure}

\begin{figure*}[tbhp]
    \includegraphics[width=0.5\linewidth]{../../plots/paper_foot_order_histogram.pdf}
\caption{The left plot is the $C=0$ case where the unbinding rate is
  independent of angle.  Here ``alternating'' means that the binding
  domain which did not move last time moved this time.  Passing means
  that the moving foot was behind, and ended up in front.}
\label{fig:steppingorder}
\end{figure*}

@@

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/paper_trajectory_plot.pdf}
\caption{\textbf{Model achieves forward-directed processivity.} \textit{Top view:} x-position of near and far binding domains during a 10 $\mu s$ simulation at high kinetic parameters of $k_b = \trajectorykb s^{-1}$ and $k_{ub} = \trajectorykub s^{-1}$. \textit{Middle view:} Cartoon snapshot of model at time indicated by bound binding domain. Teal lines correspond to the microtubule. \textit{Bottom view:} y-projection. Arrows on top and bottom plots correspond to respective snapshot times.}
\label{fig:trajectory}
\end{figure}

@@

\subsection{Elliott}
\begin{enumerate}
\item Document carefully where all figures and data comes from.
\item Describe our algorithm in sufficient detail.
\item Fix stepping analysis python module to categorize zero-length
  steps separately from other steps, particularly in terms of stepping
  times.  Alternately, change C++ to make it possible to identify
  which foot lifted if it didn't move.
\item Update plotting scripts to use stepping analysis python module,
  or other modules.
\item Write up how we estimate one-bound/bothbound time ratio from
  processivity.  Ensure simulation obeys this?
\item Keep trying to get data from Yildiz.
\item Add force-dependent plots to compare with yildiz?
\item Figure out which of the model-em subfigures to include/remove
\end{enumerate}
